---
title: "User Interface"
author: "AY"
date: "`r format(Sys.Date())`"
output:
  html_document:
    highlight: haddock
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
      smooth_scroll: no
---

The user interface of the Viewer, which is packed with MaxQuant is located at the "Viewer" tab of the MaxQuant software (highlighted by a red rectangle). The title bar along the top has the MaxQuant logo on the left, followed by an icon that can be used to rename the session, which will be displayed and is by default **Session 1 - MaxQuant - name of the currently displayed raw file**. The ribbon of the "Viewer" tab contains three groups of functions: the **Map controls** (highlighted by a petrol blue rectangle), the **Feature controls** (highlighted by a yellow rectangle) and the **Table navigation** (highlighted by a red-brown rectangle). The functionalities of all buttons within each category can be obtained from their tooltips.

```{r  echo=FALSE, fig.cap="fasta file", fig.align="center", fig.pos="!ht"}
filename <- file.path("Figures/ribbon-edited.png")
if(exists("filename")){
  knitr::include_graphics(filename)
}
```

The Viewer window is split into four different areas: the **map view**, the **MS-feature view**, the **table view** and the **protein view**. Each view can be manipulated with the corresponding buttons. The left window with the map view and the MS-feature view can be either split horizontally or vertically by the button highlighted by the blue rectangle (screenshot above).

```{r  echo=FALSE, fig.cap="fasta file", fig.align="center", fig.pos="!ht"}
filename <- file.path("Figures/featureView.png")
if(exists("filename")){
  knitr::include_graphics(filename)
}
```


