---
title: "Getting started"
author: "AY"
date: "`r format(Sys.Date())`"
output:
  html_document:
    highlight: haddock
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
      smooth_scroll: no
---


The Viewer module can either be used to get some prior information out of generated raw files or to find some follow up things after raw files have already been processed.

# Raw files prior processing
To view MS spectra of raw files, load the files using the Load or Load folder options. 

```{r  echo=FALSE, fig.cap="fasta file", fig.align="center", fig.pos="!ht"}
filename <- file.path("Figures/loadrawfiles_wiki1.png")
if(exists("filename")){
  knitr::include_graphics(filename)
}
```

# Raw files post processing with MaxQuant
File organization is important for the correct display of annotated spectra. Raw files should be in the same folder as all index files, the mqpar.xml file and all output folders created by MaxQuant during the processing (that includes the combined folder). The easiest way to load the entire data is to load the mqpar.xml file. Make sure that the file paths are correct if using this option.

```{r  echo=FALSE, fig.cap="fasta file", fig.align="center", fig.pos="!ht"}
filename <- file.path("Figures/loadparams_wiki2.png")
if(exists("filename")){
  knitr::include_graphics(filename)
}
```